Ordinal Classification Using Partially Ordered Feature Sets

### 2025-03-02 paper/main.tex
Add files via upload

@@

@@

\section{Computational experiment}
Int this section we illustrate the algorithm for the problem of the Football Player List categorization and compare results with the alternative approaches.
\begin{figure}[h]
\begin{center}
\subfigure[Original $\bZ_0$]{\includegraphics[width=0.49\textwidth]{Z_0.jpg}}
\subfigure[Estimated $\bPsi$]{\includegraphics[width=0.49\textwidth]{Z_k.jpg}}
\caption{An example of the original matrix~$\bZ_0$ and the estimated matrix~$\bPsi$ for the problem of the Football Player List categorization}
\label{figMatrices}
\end{center}
\end{figure}
The fig.~\ref{figMatrices} shows the first stage of the proposed algorithm, an estimation of the matrix~$\bPsi$ using the matrices~$\bZ_0,\bZ_1,...,\bZ_n$.
The fig.~\ref{figMatrices} shows the original~$\bZ_0$ and the estimated~$\bPsi$ matrices for the Football Player List categorization problem. For this demonstration we construct a binary matrix~$\bZ_0$ shown at fig.~\ref{figMatrices}(a). The fig.~\ref{figMatrices}(b) shows the second stage of the algorithm for the Football Player List sample. The estimated matrix~$\bPsi$ is calculated without teacher. Every element of the matrix~$\bPsi(i,k)$ shows pairwise dominance of the objects~$\bx_k$~and~$\bx_i$.

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.49\textwidth]{fig1.png}
\caption{An example of PAVA}
\label{figMatrices}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\subfigure[The separating hyperplane is parallel to the dominant eigenvector of Class 1.]{\includegraphics[width=0.49\textwidth]{fig2.png}}
\subfigure[The separating hyperplane is perpendicular to the dominant eigenvector of Class 1.]{\includegraphics[width=0.49\textwidth]{fig3.png}}
\caption{An example of mechanism of the Householder CART reflection}
\label{figMatrices}
\end{center}
\end{figure}

@@

\section{Computational experiment}
Int this section we illustrate the algorithm for the problem of the Football Player List categorization and compare results with the alternative approaches.
\begin{figure}[h]
\begin{center}
\subfigure[Original $\bZ_0$]{\includegraphics[width=0.49\textwidth]{fig4.png}}
\subfigure[Estimated $\bPsi$]{\includegraphics[width=0.49\textwidth]{fig5.png}}
\caption{An example of the original matrix~$\bZ_0$ and the estimated matrix~$\bPsi$ for the problem of the Football Player List categorization}
\label{figMatrices}
\end{center}
\end{figure}
The fig.~\ref{figMatrices} shows the first stage of the proposed algorithm, an estimation of the matrix~$\bPsi$ using the matrices~$\bZ_0,\bZ_1,...,\bZ_n$.
The fig.~\ref{figMatrices} shows the original~$\bZ_0$ and the estimated~$\bPsi$ matrices for the Football Player List categorization problem. For this demonstration we construct a binary matrix~$\bZ_0$ shown at fig.~\ref{figMatrices}(a). The fig.~\ref{figMatrices}(b) shows the second stage of the algorithm for the Football Player List sample. The estimated matrix~$\bPsi$ is calculated without teacher. Every element of the matrix~$\bPsi(i,k)$ shows pairwise dominance of the objects~$\bx_k$~and~$\bx_i$.
